### 2021-02-27 rad-icfp-2021/simplediff.tex
minor fixes

\begin{proposition}
    Let $\Gamma\vdash$!e!: !T! be a term in the source language.\\
    Then $\Gamma \vdash \UNF$(!e!):$\Gamma\times\Delta\times$!T! in source UNF for a certain type $\Delta$. 
\end{proposition}

@@

\MH{it's currently a bit wrong. need to slightly change to match with UNF-1.}

@@

>>>>

\begin{proposition}
    Let $\Gamma\vdash$!e!: !T! be a term in the source language.\\
    Then $\Gamma \vdash \UNFSymbol$(!e!): $\Gamma\times\Delta\times$!T! in source UNF for a certain type $\Delta$. 
\end{proposition}

@@

@@

Even though the target UNF is designed to achieve this purpose, we have the Following

\begin{proposition}
    If $\Gamma \vdash$!e!: !T! in source UNF, then
    $\Dtype(Gamma)\vdash \Dsynrevsymbol$(!e!):  $\Dtype$(!T!) in target UNF.
\end{proposition}
